Supporting Information

### 2015-09-04 ms.Rmd
Sent draft

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
    dev: "CairoPDF"
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
bibliography: bib/papersLib.bibtex
---

@@

## SRA details for libaries

@@

* Rice inflorescence development
+ Branching & grain yield
+ Sequential changes in meristem activity
+ Discuss a few key genes

@@

|**Discussion: what might these patterns mean biologically?**
|**Discussion: which clusters have genes that are already candidates for panicle branching?**

@@

Because of the enrichment of TF family members in some of the gene expression clusters, geneset enrichment analysis (GSEA) was used to provide an overview of expression of transcription factors and other regulators in the meristem samples (`r I(pasteLabel("Figure ", figCount, "f_gsea"))`). Unlike soft clustering, which groups genes based on shared expression dynamics, this GSEA was used to investigate the overall strength of expression of the families based on Log~2~-fold changes (L~2~FC) in the expression of their members in each stage. These patterns are not intended to represent each member of each gene family: for example, there are several MADS genes that have lower expression in the SM than in the RM, but the test statistic for the whole MADS family was higher in the SM than in the RM. Despite this caveat, there are some notable modes of expression shared between different families that may indicate roles in inflorescence development. The most pronounced change in expression appears to occur between the RM and branch meristem samples. Several families (including TUBBY-like, GROWTH-REGULATING FACTOR, bZIP and ABI3VP1 TF genes and Aux/IAA genes) are strongly expressed in RM and lower in the other meristem types. Another group, including mTERF, MYB, SBP and FHA TF genes and SET, PHD and Jumonji regulator genes, is enriched in one or both of the PBM and ePBM/SBM samples but depleted or not enriched in the RM samples.

@@

To investigate the evolution of the MADS family in Angiosperms, their expression values in the dicots *A. thaliana* and *Solanum lycopersicum* and the monocot *O. sativa* were compared to their homology in these species.

* **Figure**: Similarity tree of MADS proteins with L2FC values between comparable samples (and dN/dS values?) for each one:
+ **rice**: rachis meristem vs. spikelet merisem.
+ **arapidospis**: inflorescence meristem vs. floret meristem.
+ **tomato**: simpodial meristem vs. floret meristem. (Need to find list of tomato MADS genes. List of ~32 MIKC domain proteins on the other plant TFDB, http://planttfdb.cbi.pku.edu.cn/)
+ (could I map the l2fc to the background of the geom_label rectangle? "The fill aesthetic controls the background colour of the label.")

@@

The primary sequences of *Arabidopsis thaliana*, *Solanum lycopersicum* and *Oryza sativa* MADS proteins were downloaded by querying Phytozome 10.3 [@Goodstein:2012ho] for the PANTHER family PTHR11945 ('MADS BOX PROTEIN') via the `biomaRt` interface [@Thomas:2003db, @Durinck:2009ki].

@@

@@

# `R sessionInfo()` (*hide*)

```{r sessionInfo, results = "asis"}
pander::pander(sessionInfo())
git <- c(paste("**git branch:**",system("git rev-parse --abbrev-ref HEAD", intern = TRUE)),
          paste("**git hash:**", system("git rev-parse HEAD", intern = TRUE)))

for (x in git){cat(x, "\n")}
```

# References (move to before *Tables*)

>>>>

---
title: Genome-wide changes in expression during inflorescence architecture development
  in rice
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
    reference_docx: csl/wordStyles.docx
  pdf_document:
    fig_caption: yes
    number_sections: yes
bibliography: bib/papersLib.bibtex
---

@@

## SRA details for libraries

@@

## Rice inflorescence development
### Branching & grain yield
### Sequential changes in meristem activity
### Discuss a few key genes?

@@

**Discussion: what might these patterns mean biologically? Which clusters have genes that are already candidates for panicle branching?**

@@

Because of the enrichment of TF family members in some of the gene expression clusters, geneset enrichment analysis (GSEA) was used to provide an overview of expression of transcription factors and other regulators in the meristem samples (`r I(pasteLabel("Figure ", figCount, "f_gsea"))`). Unlike soft clustering, which groups genes based on shared expression dynamics, this GSEA was used to investigate the overall strength of expression of the families based on Log~2~-fold changes (L~2~FC) in expression of their members in each stage. These patterns are not intended to represent each member of each gene family: for example, there are several MADS genes that have lower expression in the SM than in the RM, but the test statistic for the whole MADS family was higher in the SM than in the RM. Despite this caveat, there are some notable modes of expression shared between different families that may indicate roles in inflorescence development. The most pronounced change in expression appears to occur between the RM and branch meristem samples. Several families (including TUBBY-like, GROWTH-REGULATING FACTOR, bZIP and ABI3VP1 TF genes and Aux/IAA genes) are strongly expressed in RM and lower in the other meristem types. Another group, including mTERF, MYB, SBP and FHA TF genes and SET, PHD and Jumonji regulator genes, is enriched in one or both of the PBM and ePBM/SBM samples but depleted or not enriched in the RM samples.

@@

To investigate the evolution of the MADS family in Angiosperms, their expression profiles in the dicots *A. thaliana* and *Solanum lycopersicum* and the monocot *O. sativa* were compared to their homology in these species.

| **Figure**: Similarity tree of MADS proteins with L2FC values between comparable samples (and dN/dS values?) for each one:
| **rice**: rachis meristem vs. spikelet merisem.
| **arapidospis**: inflorescence meristem vs. floret meristem.
| **tomato**: simpodial meristem vs. floret meristem.

@@

The primary sequences of *Arabidopsis thaliana*, *Solanum lycopersicum* and *Oryza sativa* MADS proteins were downloaded by querying Phytozome 10.3 [@Goodstein:2012ho] for the PANTHER family PTHR11945 ('MADS BOX PROTEIN') via the `biomaRt` interface [@Thomas:2003db; @Durinck:2009ki].

@@

----

@@

----

# `sessionInfo` (*hide*)

```{r sessionInfo, results = "asis"}
pander::pander(sessionInfo())
git <- c(paste("**git branch:**",system("git rev-parse --abbrev-ref HEAD", intern = TRUE)),
          paste("**git hash:**", system("git rev-parse HEAD", intern = TRUE)))
cat("\n")
for (x in git){cat(x, "\n")}
```

# References (move to before **Tables**)

### 2015-09-04 si.Rmd
Sent draft

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    keep_md: yes
    number_sections: yes
    dev: "CairoPDF"
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
bibliography: bib/papersLib.bib
---

>>>>

---
title: "Supporting Information"
csl: csl/the-plant-journal.csl
header-includes: \usepackage{graphicx}
output:
  BiocStyle::html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    dev: "CairoPDF"
  pdf_document:
    fig_caption: yes
    number_sections: yes
    dev: "CairoPDF"
  word_document:
    fig_caption: yes
bibliography: bib/papersLib.bibtex
---
